\documentclass{article}

\input{../_NoteHead.tex}

\newcommand{\F}{\mathbb{F}}
\renewcommand{\O}{\mathcal{O}}
\newcommand{\m}{\mathfrak{m}}
\DeclareMathOperator{\ad}{ad}
\newcommand{\gp}{\mathrm{gp}}
\newcommand{\an}{\mathrm{an}}
\newcommand{\cont}{\mathrm{cont}}

\title{$p$-adic Locally Analytic Representations}
\author{-}

\begin{document}
\maketitle


\section{Reductive Groups over Fields}

\section{Locally Analytic Representations}
Let $L$ be a $p$-adic field, and $K/L$ an extension with valuation extended.

\subsection{Definition}
\subsubsection{The groups}
An $L$\textbf{-locally analytic group} (of dimension $d$?) is a topological group $G$ such that:\begin{itemize}
    \item it is a \textbf{locally $L$-analytic manifold} admitting an atlas consists of charts
    $G\supset U\to K^d$ where the transition maps given by locally analytic functions (i.e. locally given by power series over $L$); and
    \item the multiplication is locally analytic.
\end{itemize}

\subsubsection{The vector space}
A \textbf{semi-norm} on a vector space is a ``norm'' that is not seperated.
A vector space $V$ over a topological field $K$ is called \textbf{locally convex},
if its topology is given by a family of seminorms $\{q_i\}_{i\in I}$, i.e. $V$ is equipped with the weakest topology,
such that \begin{itemize}
\item every semi-norm $q_i : V\to\R$ is continuous,
\item for every $v\in V$, the translation map $v + (-) : V\to V$ is continuous.
\end{itemize}



(Well let's just say this is a kind of good space to make the function space more ``complete''. Normed spaces are locally convex).

Let \[V' := \Hom_{K}^\cont(V, K)\] be the continuous dual of $V$,
on which we have the \begin{itemize}
    \item \textbf{strong topology}, 
\end{itemize}

If $M$ is a locally $L$-analytic manifold,
we let $C^{\an}(G, V)$ be the set of locally analytic maps $G\to V$.
It has the topology {\color{red} what?}

\subsubsection{Locally analytic representations}
Let $G$ be a $L$-analytic group, $V$ be a locally convex Hausdorff vector space over $K$.

For a representation $\rho : G\to\GL(V)$,
we say that $v\in V$ is a \textbf{locally analytic vector},
if \[g\mapsto\rho(g)v : G\to V\]
is locally analytic.
We collect locally analytic vectors in $V$ by $V^\an$, which is a subrepresentation of $G$.
\begin{example}
    If $G = \mathbb{G}(K)$ for some algebraic group $\mathbb{G}$, then any algebraic representation is locally analytic.
    This is the case we will look at.
\end{example}

\subsection{The distribution algebras}

We assume that $L/\Q_p < \infty$, and $K$ is spherically complete.

For a locally $L$-analytic manifold $M$,
we define the \textbf{space of distributions on $M$} to be\[
D(M, K) := C^\an(M, K)'\]
the dual of locally analytic functions from $M$ to $K$.



\section{The BGG category with \texorpdfstring{$P$}{P}-action}
Let $\mathbb{T\subset B\subset G}$ be over $L$.
For each standard\footnote{
    Being standard means that $\mathbb{P\supset B}$.
} parabolic $\mathbb{P}$,
let $\mathbb{L_P}$ be the Levi containing $\mathbb{T}$.

We write $G = \mathbb{G}(L)$.
For a Lie algebra $\mathfrak{a}$ over $L$,
we denote by $U(\mathfrak{a})$ the universal enveloping of $\mathfrak{a}$ \textbf{after base change to $K$}.




\end{document}
